\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2025-10-16 manuscript/manuscript.tex
completed verson with convergence rate

Theoretically, $K_n(x)$ and the simpler correction $C_n(x)$ are
asymptotically equivalent when the series is independent or exhibits
only short-memory dependence.  The joint process of
$(F_n,\hat\theta_n)$
converges to a mean-zero Gaussian limit whose long-run covariance
aggregates autocovariances across lags.  When the circular block
bootstrap reproduces this long-run covariance, the conditional bias of
$C_n$ is of smaller order $O_p(l/n)$, where $l$ is the
block length.  The expectation centering in $K_n(x)$ removes this minor
bias exactly but does not alter the first-order limit.  Consequently,
both corrections yield the same asymptotic distribution, and differences
appear only through higher-order terms that vanish as the sample size
increases.

To evaluate the finite sample impact, we compared the two corrections
through additional simulations; see results in Section~1 in the
Supplement.  Across all sample sizes and dependence
levels considered, the empirical sizes and powers were nearly identical.
This finding supports the theoretical argument that the circular block
bootstrap already captures the leading effects of serial correlation,
leaving little residual bias for the expectation centering to remove.
The comparable results of $K_n(x)$ and $C_n(x)$ suggest that the choice
between them is largely immaterial in practice.  We therefore retain
$K_n(x)$ for theoretical completeness and consistency of presentation,
while acknowledging that either correction performs similarly in finite
samples.

@@

For this reason, we also tried implementing our algorithm using the
plug-in approach for circular bootstrap block size introduced in
\citet{politis2004automatic}. Results and a discussion of this
additional simulation are provided in Section~2
in the Supplement. We also compared empirical performance for the
block bootstrap KS test when using the $K_n(x)$ correction
versus the $C_n(x)$. The $K_n(x)$ correction was used
in the main manuscript whereas results and a discussion for the
$C_n(x)$ correction is included in the supplement.
For each setting for $F$, $\tau$, and $n$, we replicate the method
10000 times to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 10000\}$
for the test when applied to samples from the same data generating
process.

>>>>

Theoretically, $K_n(x)$ and the simpler correction $C_n(x)$ are
asymptotically equivalent when the series is independent or exhibits
only short-memory dependence.  The joint process of
$\sqrt{n}(F_n, \hat\theta_n)$ converges to an $O_p(1)$
mean-zero Gaussian limit whose long-run covariance
aggregates autocovariances across lags.  When the circular block
bootstrap reproduces this long-run covariance, the conditional bias of
the $\sqrt{n}$-scaled process associated with
$C_n$ is of smaller order $O_p(l/\sqrt{n})$ as long as $l$ is
$o(\sqrt{n})$ \citep{buhlmann1994blockwise, lahiri1999theoretical}.
The expectation centering in $K_n(x)$ removes this minor
bias exactly but does not alter the first-order limit.  Consequently,
both corrections yield the same asymptotic distribution, and differences
appear only through higher-order terms that vanish as the sample size
increases.

To evaluate the finite sample impact, we compared the two corrections
through additional simulations; see results in Section~1 in the
Supplement.  Across all sample sizes and dependence
levels considered, the empirical sizes and powers were nearly identical.
This finding supports the theoretical argument that the circular block
bootstrap already captures the leading effects of serial correlation,
leaving little residual bias for the expectation centering to remove.
The comparable results of $K_n(x)$ and $C_n(x)$ incidate that, under
the examined settings, the difference between the corrections is
small. However, this may not hold under stronger dependence, longer
block lengths, or more complex statistics, where expectation centering
could have a more noticeable effect. We retain $K_n(x)$ for theoretical
completeness and consistency of presentation, while noting that either
correction performs similarly in our simulation settings.

@@

For this reason, we also tried implementing our algorithm using the
plug-in approach for circular bootstrap block size introduced in
\citet{politis2004automatic}. Results and a discussion of this
additional simulation study are provided in Section~2
in the Supplement. We also compared empirical performance for the
block bootstrap KS test when using the $K_n(x)$ correction
versus the $C_n(x)$. The $K_n(x)$ correction was used
in the main manuscript whereas results and a discussion for the
$C_n(x)$ correction is included in the supplement.
For each setting for $F$, $\tau$, and $n$, we replicate the method
10000 times to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 10000\}$
for the test when applied to samples from the same data generating
process.

### 2025-10-16 manuscript/reply2.tex
completed verson with convergence rate

A newly added paragraph clarifies that two bias corrections $C_n$ and
$K_n$ are asymptotically equivalent under independence and
short--memory dependence.  The preference for $K_n(x)$ arises from
theoretical considerations: under serial dependence, the bootstrap
analogue of $C_n(x)$ can exhibit a small $O_p(l/n)$ conditional bias
due to cross--lag covariances between $F_n(x)$ and $\hat\theta_n$,
where $l$ is the block length.  The expectation centering in $K_n(x)$
removes this bias without changing the first--order limit, yielding a
cleaner asymptotic argument.

To examine whether this refinement provides tangible benefits, we added
simulations comparing the two corrections.  Across all dependence levels
and sample sizes considered, the empirical sizes and powers were nearly
identical.  This outcome supports the theoretical result that both
methods converge to the same limit distribution and that the additional
expectation centering in $K_n(x)$ mainly improves conceptual symmetry
rather than finite--sample performance.  We have revised
Section~2.4 accordingly and added a brief reference in the Supplement to
document these findings.

>>>>

A newly added paragraph~3 in Section~2.4
clarifies that two bias corrections $C_n$ and
$K_n$ are asymptotically equivalent under independence and
short-memory dependence.  The preference for $K_n(x)$ arises from
theoretical considerations: under serial dependence, the bootstrap
analogue of $C_n(x)$ can exhibit a small $O_p(l/\sqrt{n})$ conditional bias
due to cross-lag covariances between $F_n(x)$ and $\hat\theta_n$,
where $l = o(\sqrt{n})$ \citep{buhlmann1994blockwise,
  lahiri1999theoretical}.  The expectation centering in $K_n(x)$
removes this bias without changing the first-order limit, yielding a
cleaner asymptotic formulation.

To examine whether this refinement provides tangible benefits, we added
simulations comparing the two corrections; see Section~1 of the
Supplement. Across all dependence levels
and sample sizes considered, the empirical sizes and powers were nearly
identical.  This outcome supports the theoretical result that both
methods converge to the same limit distribution under the examined
conditions. However, we note that differences could become more
pronounced under stronger dependence, longer block lengths, or more
complex statistics. The last paragraph of Section~2.4 summarizes the
results, with a brief reference to the Supplement.
